Prospective testing for the prevalence or transience of a shock effect before it occurs

### 2021-11-11 prevalence_testing/postshocktest2021draft.tex
preliminary draft of section 2.2

@@

In this section, we motivates the relation between shock persistence testing and forecasting comparison. In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly. That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases. On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information should enjoy a smaller expected loss than any conditional mean forecast without such information does. In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted. To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.

@@

In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}. The general structure of this aggregation technique is illustrated as below. Suppose we are given a nonempty donor pool with size $n$ that consist of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed. With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does. The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool. Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not. Next, we illustrate the details of our methodology as below.

For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified. The model should describe how the shock impacts the time series. Note that the model needs not to be the same for every donor in the donor pool. However, certain conditions need to be imposed as discussed previously.  Given a model for each donor pool, we compute the unadjusted forecast and adjusted forecast. For the sake of generality, unadjusted forecast and adjusted forecast are two different principles of forecast with one ignoring the shock and the other accommodating it.  From our best knowledge, in the literature of post-shock prediction, the reliable post-shock point forecast exists only for $t=T^*+1$ when the shock occurs. The adjusted forecast and unadjusted forecast are the same for $t\leq  T^*$ whereas the adjusted forecast and unadjusted forecast differs by an adjustment that depends on the model chosen.

>>>>

\label{section2}

@@

In this section, we motivates the relation between shock persistence testing and forecasting comparison. In time series literature, under a squared error loss $L(\cdot)$, the forecast using the conditional mean is the best point forecast that minimizes the expected loss if the model is specified correctly. That being said, even if the time series does experience a shock but the shock is not persistent, the expected loss of the conditional mean forecast should converge to the minimum expected loss that any forecast can achieve as sample size increases. On the other hand, if the shock is persistent, the conditional mean forecast that incorporates the shock information and makes good use of it should enjoy a smaller expected loss than any conditional mean forecast without such information does. In other words, the problem of testing for shock persistence boils down into comparing the conditional mean forecast that is adjusted by shock information and the one that is unadjusted. To deal with this problem, we applied the forecast comparison procedure of  \cite{quaedvlieg2021multi} to conduct shock persistence testing.

@@

In this paper, we propose a new way of aggregating information from donor pool to conduct post-shock persistence testing, which is quite different from \cite{lin2021minimizing}. The general structure of this aggregation technique is illustrated as below. Suppose we are given a nonempty donor pool with size $n$ that consists of donors $\mc{T}_2, \ldots, \mc{T}_{n+1}$, whose data, including shock information, are observed. With shock information, we are able to compute unadjusted forecast that does not incorporate shock information and adjusted forecast that does.  The forecast comparison using methodology of \cite{quaedvlieg2021multi} for each donor yields a $p$-value, $p_{i+1}$ for $i$th donor in the donor pool. Given $\{p_i \colon i = 2, \ldots, n+1\}$, we propose a methodology for judging whether the shock of the time series of interest is persistent or not. Next, we illustrate the details of our methodology as below.

For each donor $\mc{T}_i$, $i = 2, \ldots, n+1$, to compare adjusted and unadjusted forecasts,  a model needs to be specified. The model should describe how the shock impacts the time series at and after a certain time point $t= T_i^* + 1$. For clarity, we refers the unadjusted forecast to the conditional mean forecast based on the part of the model that ignores shock effect; and the adjusted forecast refers to the conditional mean forecast based on the full model. Note that the model needs not to be the same for every donor in the donor pool. However, certain conditions need to be imposed as discussed previously.

 Given a model for each donor pool, we compute the unadjusted conditional mean forecast and adjusted conditional mean forecast in the framework of \cite{quaedvlieg2021multi}. As introduced in the beginning of Section \ref{section2}, for a given horizon $h$, to forecast $y_{i, t}$, we compute the two forecasts based on the information set $\mathcal{F}_{i, t-h}$ of each donor pool (i.e., the data before $t-h$) for $i = 2, \ldots, n+1$. Note that in practice, a training sample size $K_i$ should be specified for $i = 2, \ldots, n+1$ such that we use the information set $\mathcal{F}_{i, t-h-K_i + 1:t-h}$.

 Even if the data contain shock information for each donor, it is impossible to compute the adjusted conditional mean forecast based on $\mathcal{F}_{i, t-h}$ when $t -h \leq T_i^*$, i.e., we only have training data that do no have any shock information. Note that this is not a big problem when $t-h \geq T_i^* +1$ because  $\mathcal{F}_{i, t-h}$ starts to incorporate shock information. In the literature, \cite{lin2021minimizing} utilizes donor pool information to provide an unbiased estimator of the shock effect such that the adjusted  conditional mean forecast is the unadjusted one plus the shock effect estimate. However, the unbiased estimation comes with the cost of assuming certain models (in terms of first and second moments) for the shock effect across the donor pool and the method only works for additive shock effect model.  To our best knowledge, there  is no other available methods that can accommodate the case when the shock model is nonlinear. However, even if the model is misspecified, using additive shock effect model to approximate the scalar shock effect that occurs at $t=T_i^*+1$ may still help as opposed to doing nothing.
